Carbonate chemistry at Ny-Ålesund

### 2023-05-31 awipev-CO2.Rmd
minor change path totables

# MacBook
if (Sys.getenv("R_PLATFORM") == "aarch64-apple-darwin20") {
  path = "../../kDrive/Documents/experiments/exp168_awipev-CO2/"
  tables_path <- "/Users/gattuso/kDrive/Documents/publications/publications_submitted/2023_gattuso_etal_essd/revised/tables/"}
#iMac Home
if (Sys.getenv("R_PLATFORM") == "x86_64-apple-darwin20") {
  path = "../../kDrive2/Documents/experiments/exp168_awipev-CO2/"
  tables_path <- "/Users/gattuso/kDrive2/Documents/publications/publications_submitted/2023_gattuso_etal_essd/revised/tables/"}
# Samir
if (Sys.getenv("LOGNAME") == "samir") path = "../../pCloud\ Sync/exp168_awipev-CO2/"

>>>>

# MacBook
if (Sys.getenv("R_PLATFORM") == "aarch64-apple-darwin20") {
  path = "../../kDrive/Documents/experiments/exp168_awipev-CO2/"
  tables_path <- "/Users/gattuso/kDrive/Documents/publications/publications_submitted/2023_gattuso_etal_essd/revised1/tables/"}
#iMac Home
if (Sys.getenv("R_PLATFORM") == "x86_64-apple-darwin20") {
  path = "../../kDrive2/Documents/experiments/exp168_awipev-CO2/"
  tables_path <- "/Users/gattuso/kDrive2/Documents/publications/publications_submitted/2023_gattuso_etal_essd/revised1/tables/"}
# Samir
if (Sys.getenv("LOGNAME") == "samir") path = "../../pCloud\ Sync/exp168_awipev-CO2/"
